Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-03-19 ConferencePaper/DraftEdwardsWoods.Rnw
Added a metric shit ton of tables and figures.  Most need to be improved.

@@

@@

\begin{itemize}
  \item differences in structure type
  \item differnce in tenure
  \item differences in energy star controling for own rent
  \item general differences in own vs rent.  
  \item explain with split incentives story
  \item difference in age of structure
  \item differnces in hot water fuel
  \item difference in heating fuel
    \item difference in climate/location
\end{itemize}

@@

  \begin{itemize}
    \item Differnces in thermostat settings
    \item difference in cooking behavior
    \item difference in reported AC use

@@

>>>>

<<echo=false,results=tex>>=
library(xtable)
xtable(table(RECS$REGIONC,RECS$TYPEHUQ), caption="Count of Observations by Region and Structure Type", label="tab:RegionVStruct")
@

@@

<<echo=false,fig=TRUE>>=
qplot(NHSLDMEM,data=RECS,facets =~EthRace, geom = "density",title="Household Size by Race and Ethnicity")+xlab("Household Size")
@

@@

\begin{itemize}
  \item differences in structure type x
  \item differnce in tenure x
  \item differences in energy star controling for own rent
  \item general differences in own vs rent.  
  \item explain with split incentives story
  \item difference in age of structure x
  \item differnces in hot water fuel x
  \item difference in heating fuel x
    \item difference in climate/location x
\end{itemize}

<<echo=false, results=tex>>=
xtable(table(RECS$EthRace,RECS$UR),caption="Race by Urban/Rural", label="tab:UrbRural")
@

<<echo=false, results=tex>>=
xtable(table(RECS$EthRace,RECS$ESWWAC),caption="EnergyStar Wall AC by Race and Ethnicity", label="tab:EstarWall")
@

<<echo=false, results=tex>>=
xtable(table(RECS$EthRace,RECS$UR),caption="Race by Urban/Rural", label="tab:UrbRural")
@

<<echo=false, results=tex>>=
xtable(table(RECS$EthRace,RECS$FUELH2O),caption="Water Service by Race and Ethnicity", label="tab:Water")
@

<<echo=false, results=tex>>=
xtable(table(RECS$EthRace,RECS$FUELHEAT),caption="Heating Fuel by Race and Ethnicity", label="tab:HeatFuel")
@

<<echo=false, results=tex>>=
xtable(table(RECS$EthRace,RECS$Climate_Region_Pub),caption="Climate by Race and Ethnicity", label="tab:Climate")
@

\begin{figure}
\begin{center}
\caption{Age of Structure by Rent/Own and Race/Ethnicity}
\label{fig:AgebyOwnRace}
<<echo=false,fig=TRUE>>=
qplot(YEARMADE,data=RECS,facets =KOWNRENT~EthRace, geom = "density",)
@
\end{center}
\end{figure}

@@

  \begin{itemize}
    \item Differnces in thermostat settings
    \item difference in cooking behavior x
    \item difference in reported AC use

@@

<<echo=false, results=tex>>=
xtable(table(RECS$EthRace,RECS$NUMMEAL),caption="Weekly Meals Cooked by Race and Ethnicity", label="tab:Cooking")
@

\begin{figure}
\begin{center}
\caption{Daytime Temp and Race/Ethnicity (Winter)}
\label{fig:TempHomeRace}
<<echo=false,fig=TRUE>>=
boxplot(TEMPHOME~EthRace, notch=TRUE,data=RECS)
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Daytime Temp When Away and Race/Ethnicity (Winter)}
\label{fig:DayAwayRace}
boxplot(TEMPGONE~EthRace, notch=TRUE,data=RECS)
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Nightime Temp and Race/Ethnicity (Winter)}
\label{fig:NightRace}
<<echo=false,fig=TRUE>>=
boxplot(TEMPNITE~EthRace, notch=TRUE,data=RECS)

@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Daytime Temp Home by Race/Ethnicity (Summer)}
\label{fig:NightRaceS}
<<echo=false,fig=TRUE>>=
boxplot(TEMPHOMEAC~EthRace, notch=TRUE,data=RECS)

@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Day Temp Away by Race/Ethnicity (Summer)}
\label{fig:NightRaceS}
<<echo=false,fig=TRUE>>=
boxplot(TEMPGONEAC~EthRace, notch=TRUE,data=RECS)

@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Nightime Temp and Race/Ethnicity (Summer)}
\label{fig:NightRaceS}
<<echo=false,fig=TRUE>>=
boxplot(TEMPNITEAC~EthRace, notch=TRUE,data=RECS)
@
\end{center}
\end{figure}
